---
title: "MAGIC PARKING SYSTEM"
author: 'MIS-620 Analysis and Design of Information Systems | Team: Magic Parking'
date: "November 2, 2016"
output: pdf_document
---

```{setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Overview of the system

Magic Parking is a software platform to make physical parking spaces available online for reservation. It includes following key functionalities 

* Parking space owner can make the space available online with Magic Parking
* Customers can search for parking around them or at particular location and reserve them if available


## 2.Tools and methods used to implement

We intend to develop above system as a ubiquitous web application. We are also looking forward to integrate our web application with Android and iOS. We considered using following technologies/tools/techniques to achieve the system functionalities.

#####2.1 Internet Technologies:
+ Client Side: HTML5, CSS3, Bootstrap3, Jquery1.11.1
+ Server Side: Php5.x
+ Database: MySQL
+ Test Server: WAMP3.0.6

#####2.2 Hardware details:
+ Programming Language: Embedded C
+ Processor: Atmega328 8 bit micro controller
+ Clock speed: 8 MHz
+ Voltage: 3.3v 
+ Wi-Fi module: ESP8266
+ Sensor: Ultrasonic range finder - SR04


## 3.Creating database and tables in MySQL

There are 9 Classes in our class diagram and they can be converted into corresponding database tables using the following code

Create and select the database
```{r echo=TRUE, eval=FALSE}
CREATE DATABASE magicParking
```
```{r echo=TRUE, eval=FALSE}
USE magicParking
```

Now create the table for Customer

```{r echo=TRUE, eval=FALSE}
CREATE TABLE CUSTOMER(
        user_id int unsigned auto_increment,
        fname varchar(30) NOT NULL,
        lname varchar(30) NOT NULL,
        email varchar(40) UNIQUE NOT NULL,
        pass varchar(40) NOT NULL,
        is_verified enum('TRUE','FALSE') NOT NULL DEFAULT 'FALSE',
        otp varchar(30) NOT NULL,
        phone varchar(15) DEFAULT NULL,
        car_num varchar(15) DEFAULT NULL,
        car_type enum('sedan','suv','hatchback','minivan/van','truck','convertible') DEFAULT NULL,
        can_reserve enum('TRUE','FALSE') NOT NULL DEFAULT 'FALSE',
        PRIMARY KEY(user_id)
        )ENGINE=InnoDB

```

Create table for the parking space owner

```{r echo=TRUE, eval=FALSE}
CREATE TABLE OWNER(
    user_id int unsigned AUTO_INCREMENT,
    fname varchar(30) NOT NULL,
    lname varchar(30) NOT NULL,
    email varchar(40) UNIQUE NOT NULL,
    pass varchar(40) NOT NULL,
    otp varchar(30) NOT NULL,
    is_verified enum('TRUE','FALSE') NOT NULL DEFAULT 'FALSE',
    orgname varchar(20),
    address varchar(20) NOT NULL,
    zipcode varchar(5) NOT NULL,
    state varchar(15) NOT NULL,
    city varchar(15) NOT NULL,
    PRIMARY KEY (user_id)
    )ENGINE=InnoDB

```

Create table for the parking lot monitor

```{r echo=TRUE, eval=FALSE}
CREATE TABLE MONITOR(
        user_id int unsigned AUTO_INCREMENT,
        fname varchar(30) NOT NULL,
        lname varchar(30) NOT NULL,
        email varchar(40) UNIQUE NOT NULL,
        pass varchar(40) NOT NULL,
        otp varchar(30) NOT NULL,
        is_verified enum('TRUE','FALSE') NOT NULL DEFAULT 'FALSE',
        owner_id int unsigned NOT NULL,
        phone varchar(15) NOT NULL,
        PRIMARY KEY (user_id),
        FOREIGN KEY (owner_id) REFERENCES OWNER(user_id)
        ON DELETE CASCADE
        )ENGINE=InnoDB

```

Create table to store the parking space details

```{r echo=TRUE, eval=FALSE}
CREATE TABLE PARKINGSPACES(
    space_name varchar(10) NOT NULL,
    owner_id int unsigned NOT NULL,
    lat varchar(10) NOT NULL,
    lon varchar(10) NOT NULL,
    altitude int NOT NULL,
    accuracy int NOT NULL,
    PRIMARY KEY (lat,lon,altitude),
    FOREIGN KEY (owner_id) REFERENCES OWNER(user_id)
    ON DELETE CASCADE
    )ENGINE=InnoDB

```

Create table to store the parking space availability

```{r echo=TRUE, eval=FALSE}
CREATE TABLE AVAILABILITY(
        space_id int unsigned auto_increment,
        lat varchar(10) NOT NULL,
        lon varchar(10) NOT NULL,
        altitude int NOT NULL,
        is_occupied enum('YES','NO') DEFAULT 'YES',
        is_reserved enum('YES','NO') DEFAULT 'NO',
        PRIMARY KEY(space_id),
        FOREIGN KEY(lat,lon,altitude) REFERENCES parkingspaces(lat,lon,altitude)
        ON DELETE CASCADE
        )ENGINE=InnoDB

```

Create table to store sensor details

```{r echo=TRUE, eval=FALSE}
CREATE TABLE SENSORS(
        sensor_id int unsigned auto_increment,
        space_id int unsigned NOT NULL,
        reg_ip varchar(20) NOT NULL,
        state enum('Occupied','vacant','disabled'),
        PRIMARY KEY(sensor_id),
        FOREIGN KEY(space_id) REFERENCES AVAILABILITY(space_id)
        ON DELETE CASCADE
        )ENGINE=InnoDB

```

Create table to store ticket details

```{r echo=TRUE, eval=FALSE}
CREATE TABLE TICKETS(
        ticket_id int unsigned auto_increment,
        user_id int unsigned not null,
        space_id int unsigned not null,
        time_of_booking datetime not null,
        check_in_time datetime not null,
        check_out_time datetime not null,
        state enum('booked','cancelled','suspended','finished') default 'booked',
        extended_check_out datetime default NULL,
        PRIMARY KEY(ticket_id),
        FOREIGN KEY(user_id) references customer(user_id) on delete cascade,
        FOREIGN KEY(space_id) references availability(space_id) on delete cascade
        )ENGINE=InnoDB

```

Create table to store complaints from customers

```{r echo=TRUE, eval=FALSE}
CREATE TABLE COMPLAINTS(
        report_id int unsigned auto_increment,
        ticket_id int unsigned not null,
        time_reported datetime not null,
        complaint_status enum('placed','resolved') default 'placed',
        PRIMARY KEY(report_id),
        FOREIGN KEY(ticket_id) references tickets(ticket_id)
        ON DELETE CASCADE
        )ENGINE=InnoDB

```

Finally, create table to store notifications data

```{r echo=TRUE, eval=FALSE}
CREATE TABLE NOTIFICATIONS(
        notif_id int unsigned auto_increment,
        ticket_id int unsigned not null,
        remind_at datetime not null,
        notif_status enum('active','expired') default 'active',
        PRIMARY KEY(notif_id),
        FOREIGN KEY(ticket_id) references tickets(ticket_id)
        ON DELETE CASCADE
        )ENGINE=InnoDB

```